---
title: "Assignment_06"
author: "Praveen Kenderla"
date: "April 8, 2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
header-includes: \DeclareMathSizes{12}{12}{12}{12}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading Libraries:

******
```{r, message = FALSE, warning = FALSE, results = 'hide', include=TRUE}
library(tidyverse)
library(ggmap)
library(ggplot2)
library(maps)
library(magick)
```
******

## 1. Draw Road Map and Water Map 
******
```{r, message= FALSE, warning = FALSE, results = 'hide', fig.height =4}

BudeRoadMap <- get_googlemap(center = c(-4.543678, 50.82664), maptype = "roadmap", zoom = 13)
ggmap(BudeRoadMap) # Drawing roadmap of Bude West England
dev.copy(png,'BudeRoadMap.png')
dev.off()
saveRDS(BudeRoadMap, "BudeRoadMap.RDS")


```
******

## 1. Draw Road Map and Water Map (continued..) 

******
```{r, results = 'hide', message= FALSE, warning = FALSE, fig.keep = 'all', fig.height =4}

BudeWaterMap <- get_map("Bude england",source = "stamen", maptype = "watercolor", zoom = 13)
ggmap(BudeWaterMap) # Drawing WaterMap of Bude West England
dev.copy(png,'BudeWaterMap.png')
dev.off()
saveRDS(BudeWaterMap, "BudeRoadMap.RDS")

```
******


## 2. Identify locations in Bude

******
```{r, results = 'hide', message= FALSE, warning = FALSE, fig.keep = 'all', fig.height =4}

A <- geocode("Bude West England")
B <- get_map(A, zoom = 12)

BWaterMap <- get_map(A, source = "stamen", maptype = "watercolor", zoom = 13)

# Locations in the Bude 
L1 <- geocode("Bude Sea Pool,bude")
L2 <- geocode("Bude Beaches,bude")
L3 <- geocode("Bude North Cornwall Cricket Club,bude")
L4 <- geocode("Bar 35,bude")

LRowCombi <- rbind(L1, L2, L3)   # Combing all co-oridnates for 3 locations
```

******

## 2. Identify locations in Bude (Continued...)


### Drawing red dots in the concered locations both in Water Map and Road Map. 


******
```{r, results = 'hide', message= FALSE, warning = FALSE, fig.keep = 'all', fig.height =4}

BWaterMap <- ggmap(BudeWaterMap) + geom_point(aes(x = lon, y = lat), data = LRowCombi, color = "red", size = 2) 
BWaterMap 

dev.copy(png,'BWaterMap.png')
dev.off()
saveRDS(BudeRoadMap, "BWaterMap.RDS")


BRoadMap <- ggmap(BudeRoadMap) + geom_point(aes(x = lon, y = lat), data = LRowCombi, color = "red", size = 2)
BRoadMap

dev.copy(png,'BRoadMap.png')
dev.off()
saveRDS(BudeRoadMap, "BRoadMap.RDS")
```

******


## 3. Drawing path between cricket ground and Pub


******
```{r, results = 'hide', message= FALSE, warning = FALSE, fig.keep = 'all', fig.height =4}

Q <- geocode("Bude North Cornwall Cricket Club, Bude")
QMap1 <- get_googlemap(center = c(-4.552814, 50.83347), maptype = "roadmap", zoom = 15)

QMap2 <- ggmap(QMap1) + geom_point(aes(x = lon, y = lat), data = Q, color = "red", size = 2)
QMap2

W <- geocode("Bar 35, Bude")
WMap1 <- get_googlemap(center = c(-4.544088, 50.83016), maptype = "roadmap", zoom = 15 )

WMap2 <- ggmap(WMap1) + geom_point(aes(x = lon, y = lat), data = W, color = "red", size = 2)
WMap2
```
******

### 3. Drawing path between cricket ground and Pub(continued)


******
```{r, results = 'hide', message= FALSE, warning = FALSE, fig.keep = 'all', fig.height =4}

from <- "Bude North Cornwall Cricket Club, Bude" 
to <- "Bar 35,bude"

route_df <- route(from, to, structure = "route")
#trek_df  <-  trek(from, to, structure = "route")


QW <- rbind(Q,W)

QW1 <- ggmap(WMap1) + geom_point(aes(x = lon, y = lat), data = QW, color = "red", size = 2)

QW1

Names <- c("Circket ground", "Bude Pub")
```
******

### 3. Drawing path between cricket ground and Pub (Continued...)

******
```{r, results = 'hide', message= FALSE, warning = FALSE, fig.keep = 'all', fig.height =4}

QW2 <- ggmap(WMap1) + 
       geom_point(aes(x = lon, y = lat), data = QW, 
                  color = "red", size = 2) +  
        geom_text(aes(x = lon, y = lat), data = QW, label = Names) +
        
      geom_path(
         aes(x = lon, y = lat), color = "blue", 
          size = 1.5, alpha = .5,
            data = route_df, lineend = "round"
        ) + 
       geom_path(
         aes(x = lon, y = lat), color = "red",
           size = 1.5, alpha = .5, 
             data = route_df, lineend = "round"
        ) 

RouteMap <- QW2
RouteMap # Path between the cricket club and the Bude Pub

dev.copy(png,'RouteMap.png')
dev.off()

saveRDS(BudeRoadMap, "RouteMap.RDS")

```
******
